---
title: "Association Rules"
author: "shinyarah"
date: "7/16/2021"
output: html_document
---

```{r}
library(arules)
```
## LOADING OUR DATASET
```{r}
path <-"http://bit.ly/SupermarketDatasetII"

Transactions<-read.transactions(path, sep = ",")
Transactions
```
## READING OUR DATASET
```{r}
# Verifying the object's class

class(Transactions)
```
```{r}
#previewing our dataset
head(transactions)
```

```{r}
tail(transactions)
```


```{r}
# Generating a summary of the transaction dataset

summary(Transactions)
```




```{r}
#structure
str(transactions)
```

```{r}
dim(transactions)
```


## SOLUTION IMPLEMENTATION
```{r}
# chart of frequencies and filtering that considers items with a minimum percentage 
par(mfrow = c(1, 2))

# plot the frequency of items
itemFrequencyPlot(Transactions, topN = 10,col="red")
itemFrequencyPlot(Transactions, support = 0.1,col="brown")
```

```{r}
# Building a model based on association rules 
# using the apriori function 
# ---
# We use Min Support as 0.001 and confidence as 0.8
rules <- apriori (Transactions, parameter = list(supp = 0.001, conf = 0.8))
rules
```
using a confidence of 0.8 and min support = 0.001 gives us 74 rules 


```{r}
# Building a apriori model with Min Support as 0.002 and confidence as 0.8.
rules2 <- apriori (Transactions,parameter = list(supp = 0.002, conf = 0.8)) 

# Building apriori model with Min Support as 0.002 and confidence as 0.6.
rules3 <- apriori (Transactions, parameter = list(supp = 0.001, conf = 0.6)) 

rules2

rules3
```

```{r}
# performing an exploration of our model 
# 
summary(rules)
```

```{r}
# Observing rules built in our model i.e. first 5 model rules
# 
inspect(rules[1:5])
```

Rule 1: if someone buys french fries, mushroom cream sauce and pasta, they are more likely to buy escalope

```{r}
# next we order these rules by level of confidence
# 
rules<-sort(rules, by="confidence", decreasing=TRUE)
inspect(rules[1:8])
```

```{r}
# If we're interested in making a promotion relating to the sale of mineral water, 
# we could create a subset of rules concerning these products 
# ---
# This would tell us the items that the customers bought before purchasing mineral water
# ---
# 
mineral_water <- subset(rules, subset = rhs %pin% "mineral water")
 
# Then order by confidence
mineral_water<-sort(mineral_water, by="confidence", decreasing=TRUE)
inspect(mineral_water[1:5])
```


## RECOMMENDATIONS
1. stock french fries,mushroom cream sauce,pasta with escalope as they have the highest association
3. there is a tendency for customers to buy protein-rich food together. these shouls be stocked together to maximamize sales.
3. the most common transations were with 1 item (1754 items), followed by those with 2 and 3 items.
4. place eggs, meatballs, pasta, cake, minearl water and milk should be closely arranged as they present a high confidence of being purchased together.
5. Top 5 items purchased are: mineral water, eggs, pasta, french fries, chocolate.
6. Escalope should have a targeted promotion especially with customers that purchased french fries,mushroom cream sauce and pasta.
 


